\sick, the spectroscopic inference crank

### 2014-08-09 document/manuscript.tex
Cave man not invent word wrap yet. Make look good for cave man.

\section{Introduction}
Most of our understanding of astrophysics has been interpreted from spectra. Given how informative spectroscopic data is to our understanding of astrophysics, it is not surprising that the last decade has seen a substantial increase of publicly accessible spectral data. Large scale surveys have driven this trend, each releasing in excess of hundreds of thousands \citep[e.g.,][]{wigglez,boss,segue,rave,gaia-eso} of spectra. Millions more spectra are expected in the coming years \citep[e.g.,][]{lamost,galah}.

@@

With all of the combined effects there are 16 free parameters including $\bm{\psi}$, our astrophysical quantities of interest. For the examples presented in Section \ref{sec:examples}, this requires interpolation between 92 billion pixels in four dimensions. While the description might appear daunting, the problem is tractable, numerically efficient, and easy to configure. By default \sick{} numerically solves this problem in three sequential steps, which are described in the following sections: scattering, optimisation, and Monte-Carlo Markov Chain (MCMC) sampling.

@@

% The AMBRE synthetic spectra have been calculated using 1D MARCS model atmospheres and synthesised using Turbospectrum \citep{turbospectrum} under the assumption of local thermal equilibrium (LTE). There are 28,344 permutations of effective temperature $T_{\rm eff}$, surface gravity $\log{g}$, overall metallicity $[{\rm M/H}]$ and mean $\alpha$-element enhancement $[\alpha/{\rm Fe}]$. The typical step size is 250 K in temperature, 0.25 dex in $\log{g}$, 0.25 dex in [Fe/H] and 0.10 dex in [$\alpha$/Fe]. Each grid point has synthesised continuum-normalised intensities between [0, 1]  for two spectral channels: one from 475\,nm to 685\,nm, and a redder channel covering 845\,nm to 895\,nm. Both channels are sampled at approximately $\sim4\times10^{-4}$\,nm, yielding more than $92\times10^9$ pixels.

@@

\subsection{Sol}
\label{sec:sun}
A high-resolution ($\mathcal{R} \sim$ 20000), high S/N ($\sim{}$150 pixel$^{-1}$) twilight spectrum was obtained from the GIRAFFE/FLAMES archive\footnote{https://www.eso.org/observing/dfo/quality/GIRAFFE/pipeline/solar.html}. The H875.7 setup was chosen for this example, yielding spectra from 848.2\,nm to 899.2\,nm. Data points redder than 874\,nm have been discarded to more closely match the Gaia RVS wavelength coverage, and demonstrate the recoverability of stellar parameters on real data.

>>>>

\section{Introduction}
Most of our understanding of astrophysics has been interpreted from spectra. 
Given how informative spectroscopic data is to our understanding of astrophysics, 
it is not surprising that the last decade has seen a substantial increase of 
publicly accessible spectral data. Large scale surveys have driven this trend, 
each releasing in excess of hundreds of thousands \citep[e.g.,][]{wigglez,boss,
segue,rave,gaia-eso} of spectra. Millions more spectra are expected in the 
coming years \citep[e.g.,][]{lamost,galah}.

@@

With all of the combined effects there are 16 free parameters including $\bm{\psi}$, 
the astrophysical quantities of interest. For the examples presented in Section 
\ref{sec:examples}, this requires interpolation between 92 billion pixels in four 
dimensions. While the description might appear daunting, the problem is tractable, 
numerically efficient, and easy to configure. By default \sick{} numerically solves 
this problem in three sequential steps, which are described in the following 
sections: scattering, optimisation, and Monte-Carlo Markov Chain (MCMC) sampling.

@@

@@

\subsection{Sol}
\label{sec:sun}
A high-resolution ($\mathcal{R} \sim$ 20000), high S/N ($\sim{}$150 pixel$^{-1}$) 
twilight spectrum was obtained from the GIRAFFE/FLAMES archive
\footnote{https://www.eso.org/observing/dfo/quality/GIRAFFE/pipeline/solar.html}. 
The H875.7 setup was chosen for this example, yielding spectra from 848.2\,nm to 
899.2\,nm. Data points redder than 874\,nm have been discarded to more closely 
match the Gaia RVS wavelength coverage, and demonstrate the recoverability of 
stellar parameters on real data.
